Solving the Poisson-equation in one dimension \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-09-15 Project1/article/article.tex
Results part shaping up

\begin{table}[h]
\caption{Elapsed time for different $n$}
\begin{tabular}{lcc}
\hline
n & TDMA [s] & LU [s] \\ \hline
10 & 0.0000035 & 0.00312535 \\
100 & 0.0000116 & 0.00193754 \\
1000 & 0.000077892 & 0.0677764 \\
10000 & 0.000878769 & 21.9247 \\
100000 & 0.00757418 & n/a \\
1000000 & 0.08616075 & n/a \\
10000000 & 0.76534 & n/a
\end{tabular}
\label{tab:solver_times}
\end{table}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/10.png}
  \caption{Numerical approximation for $n=10$}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/100.png}
  \caption{Numerical approximation for $n=100$}
\end{figure}

\section{Discussion}

>>>>

The run time for the optimized tridiagonal matrix algorithm and the LU
decomposition solver is in table \ref{tab:solver_times}. The reason
run times are not given for $n>10000$ for the LU method is because the
method uses too much memory for the solver to even
function. Regardless, the message of table \ref{tab:solver_times} is
quite clear, the specialized tridiagonal matrix method is vastly more
efficient.

\begin{table}[h]
\caption{Elapsed time for increasing $n$}
\begin{tabular}{lcc}
\hline
n & TDMA [s] & LU [s] \\ \hline
10 & 0.0000035 & 0.00106083 \\
100 & 0.0000116 & 0.0022319 \\
1000 & 0.000077892 & 0.0677764 \\
10000 & 0.000878769 & 21.9247 \\
100000 & 0.00757418 & n/a \\
1000000 & 0.08616075 & n/a \\
10000000 & 0.76534 & n/a
\end{tabular}
\label{tab:solver_times}
\end{table}

Tables \ref{fig:n10} and \ref{fig:n100} show the fit of the
tridiagonal matrix solver for $n=10$ and $n=100$, respectively. One
can easily see that already at $n=100$ the fit is already very
good.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/10.png}
  \caption{Numerical approximation of the tridiagonal matrix algorithm for $n=10$}
  \label{fig:n10}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/100.png}
  \caption{Numerical approximation of the tridiagonal matrix algorithm for $n=100$}
  \label{fig:n100}
\end{figure}

Figure \ref{fig:relerror} shows a plot of the maximum relative error of the
tridiagonal solver as a function of step size. One can see that the
relative error falls as the step size falls, but only to a certain
point. By decreasing the step size further the error increases, most
likely because of decreasing numerical precision because of the
computers difficulty in representing very small numbers.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{figures/relerror.png}
  \caption{Plot of maximum relative error as a function of step size}
  \label{fig:relerror}
\end{figure}
\section{Discussion}
